---
title: "Homework MD 06"
author: "Terry Moore"
embed-resources: true
format: html
editor: visual
---

# Homework 6.2

For this assignment you are going to use the `bikes` dataset we began analyzing in class. You can get that dataset from the **bayesrules** package. Once **bayesrules** is installed, you can begin.

``` r
library(tidyverse)
library(moderndive)
theme_set(theme_minimal())
```

```{r}
#| message: false
library(tidyverse)
library(broom)
library(moderndive)
theme_set(theme_minimal())

```

Load the data and take a look.

``` r
data(bikes, package = "bayesrules")
glimpse(bikes)
```

```{r}
#| message: false
data(bikes, package = "bayesrules")
glimpse(bikes)
```

```         
## Rows: 500
## Columns: 13
## $ date        <date> 2011-01-01, 2011-01-03, 2011-01-04, 2011-01-05, 2011-01-0…
## $ season      <fct> winter, winter, winter, winter, winter, winter, winter, wi…
## $ year        <int> 2011, 2011, 2011, 2011, 2011, 2011, 2011, 2011, 2011, 2011…
## $ month       <fct> Jan, Jan, Jan, Jan, Jan, Jan, Jan, Jan, Jan, Jan, Jan, Jan…
## $ day_of_week <fct> Sat, Mon, Tue, Wed, Fri, Sat, Mon, Tue, Wed, Thu, Fri, Sat…
## $ weekend     <lgl> TRUE, FALSE, FALSE, FALSE, FALSE, TRUE, FALSE, FALSE, FALS…
## $ holiday     <fct> no, no, no, no, no, no, no, no, no, no, no, no, no, yes, n…
## $ temp_actual <dbl> 57.39952, 46.49166, 46.76000, 48.74943, 46.50332, 44.17700…
## $ temp_feel   <dbl> 64.72625, 49.04645, 51.09098, 52.63430, 50.79551, 46.60286…
## $ humidity    <dbl> 80.5833, 43.7273, 59.0435, 43.6957, 49.8696, 53.5833, 48.2…
## $ windspeed   <dbl> 10.749882, 16.636703, 10.739832, 12.522300, 11.304642, 17.…
## $ weather_cat <fct> categ2, categ1, categ1, categ1, categ2, categ2, categ1, ca…
## $ rides       <int> 654, 1229, 1454, 1518, 1362, 891, 1280, 1220, 1137, 1368, …
```

## 

Before analyzing a dataset, it's good to know some stuff about it. Answer the following questions:

how many rows are in the dataset?

-   **500**

    what does each row represent?

    **Each row represents a day.**

    what dates does the dataset cover?

    **It covers dates from 01/01/2011 to 12/31/2012.**

    what is the highest observed ridership in the dataset?

    **Highest observed ridership in the dataset is 6,946.**

    what was the highest wind speed recorded in the dataset?

    **34.00002.**

## Question 1

What is the correlation between number of rides and what the temperature feels like (in Fahrenheit)? What is the correlation between the number of rides and wind speed (miles per hour)?

```{r}
bikes |>
  select(rides, temp_feel) |>
  cor()
```

There is a positive correlation of .582 between number of rides and what the temperature feels like in Fahrenheit.

```{r}
bikes |>
  select(rides, windspeed) |>
  cor()
```

There is a negative correlation of -.195 between number of rides and the wind speed in miles per hour.

## Question 2

Using the approximation that a mile is equal to 1.61 kilometers, convert `windspeed` to kilometers per hour. Call the new variable `wind_kph` and add it to the `bikes` data frame. What is the correlation between wind speed in MPH and wind speed in KPH? Explain why in enough detail that I know you understand.

```{r}
bikes <- bikes |>
    mutate(wind_kph = windspeed*1.61)
```

```{r}
bikes |>
  select(windspeed, wind_kph) |>
  cor()
```

The correlation between wind speed in MPH is one, and the correlation between wind speed in KPH is also one. This is because the two variables are the same.

## Question 3

Estimate two simple regressions:

-   predict rides as a function of wind speed in MPH

```{r}
#Fit regression model
simple_MPH <- lm(rides ~ windspeed, data = bikes)

#Get regression table
broom::tidy(simple_MPH)
```

-   predict rides as a function of wind speed in KPH

```{r}
#Fit regression model
simple_KPH <- lm(rides ~ wind_kph, data = bikes)

#Get regression table
broom::tidy(simple_KPH)
```

Use `get_regression_table()` or `broom::tidy()` to display the results. This will give you two sets of an intercept and a slope. If any coefficients are the same between models, explain why. If any coefficients are different between models, explain why. Make sure to give me enough detail to convince me you understand.

For the first regression (wind in mph), it shows that each 1 mph increase in wind speed produces 56 fewer bike rides. For the second regression (wind in kph), it shows that each 1 kph increase in wind speed produces 34 fewer bike rides.

The coefficients are different between models because the units of one is in miles per hour for one predictor and in kilometers per hour for the other. The intercepts are equal, which means they have equal origins. Also, the slope coefficients are numerically different due to the different units selected, but can be set equal to each other if the units are converted to like terms. For instance, a mile is equal to 1.61 kilometers, so the slope for wind-speed in MPH should be the slope for wind-speed in KPH, divided by 1.61. (55.52268/1.61 = -34.48614)

## Question 4

Using the models from above, tell me what the predicted ridership would be if the wind is blowing at 20 KPH. What would the predicted ridership be if the wind is blowing at 20 MPH?

```{r}
pred_df_simple_KPH <- tribble(~wind_kph, 20)

pred_df_simple_KPH <- pred_df_simple_KPH |>
  mutate(exp_rides = predict(simple_KPH, newdata = pred_df_simple_KPH)) |>
  select(exp_rides)
pred_df_simple_KPH
```

The predicted ridership if the wind is blowing at 20 KPH would be 3515 rides.

```{r}
pred_df_simple_MPH <- tribble(~windspeed, 20)

pred_df_simple_MPH <- pred_df_simple_MPH |>
  mutate(exp_rides = predict(simple_MPH, newdata = pred_df_simple_MPH)) |>
  select(exp_rides)
pred_df_simple_MPH
```

The predicted ridership if the wind is blowing at 20 MPH would be 3095 rides.

## Question 5

Let's get more realistic and move to multiple regression. We're going to use `temp_feel` in addition to wind speed. But we don't want to use Fahrenheit. So make a new variable called `temp_c` that is a conversion of `temp_feel` to Celsius and add it to the `bikes` dataframe. (You may have to look up how to do this conversion.)

```{r}
bikes <- bikes |>
  mutate(temp_c = 5/9 * (temp_feel - 32))
```

With this new variable, estimate a multiple regression that predicts rides as an additive function of `wind_kph` and `temp_c` (that is, no interaction). Interpret both of the slope coefficients using the following language:

"For a \_\_\_\_\_ increase in \_\_\_\_\_, the model expects a \_\_\_\_\_ increase in \_\_\_\_\_."

```{r}
#Fit regression model
additive_model <- lm(rides ~ wind_kph + temp_c, data = bikes)

#Get regression table
broom::tidy(additive_model)
```

Now interpret the intercept.

For a 1 degree in celsius increase in temperatue, the model expects a 143.23 increase in in rides. For a 1 kilometer per hour increase in wind speed, the model expects a 19.84 decrease in in rides. When no wind speed is present and the temperature is at freezing point (0 degrees celsius), the model expects 942 rides.

## Question 6

Using the multiple regression you just estimated, give me ridership predictions for the following situations:

-   SITUATION 1: temp = 25C, wind = 15 KPH
-   SITUATION 2: temp = 15C, wind = 5 KPH
-   SITUATION 3: temp = 10C, wind = 40 KPH

You can do this manually (using R as a calculator) or you might find the following code useful. I'm not going to give you *all* the code, but this is a head start!

```{r}
pred_df <- tibble(
  situation = 1:3,
  temp_c = c(25, 15, 10),
  wind_kph = c(15, 5, 40)
)

pred_df <- pred_df |>
  mutate(expected_ridership = predict(additive_model, newdata = pred_df)) |>
  select(situation, expected_ridership)

pred_df
```

Answer: (rounded to the nearest hundredth)

Situation 1: 4225.65

Situation 2: 2991.73

Situation 3: 1581.08

## Question 7

Let's add another predictor into the mix. Estimate a new model that uses `weekend` in addition to the predictors already in the model. Display the model results. Interpret the coefficient on `weekend` using a complete sentence.

```{r}
#Fit regression model
additive_model_weekend <- lm(rides ~ wind_kph + temp_c + weekend, data = bikes)

#Get regression table
broom::tidy(additive_model_weekend)
```

When it is true that it is the weekend, the model expects the ridership to decrease by 714 rides.

## Question 8

If the temperature and the wind speed are average, what is the expected ridership for a weekend day? What is the expected ridership for a weekday? Show the code that gets you your answers.

```{r}
avg_sets <- bikes |>
  summarise(avg_temp = mean(temp_c),
            avg_windspeed = mean(wind_kph))
avg_sets
```

```{r}
pred_wknd <- avg_sets |>
  mutate(rs = 1214.80251 - 20.38598*avg_windspeed + 140.33863*avg_temp - 713.57504) |>
  select(rs)

pred_wknd
```

```{r}
pred_wday <- avg_sets |>
  mutate(rs = 1214.80251 - 20.38598*avg_windspeed + 140.33863*avg_temp) |>
  select(rs)

pred_wday
```

## Question 9

You can use `get_regression_points()` or `predict()` to see how the model did at predicting each individual value of `rides`. Use one of these functions to find the date with the *largest absolute residual*. That is, find the day where the model is most wrong about predicted ridership. Why is the model so wrong about this day? (There is a correct answer here.)

```{r}
regression_p <- get_regression_points(additive_model_weekend)

regression_p |>
  arrange(residual)
```

The date with the largest absolute residual was 10/29/2012 with a residual of -3490.348. I saw that it was the same day as Hurricane Sandy hitting the United States. The harsh weather that likely appeared at Washington D.C. reduced the amount of people that were riding bikes that day.
