---
title: dv 5
author: Terry Moore
format: html
embed-resources: true
editor: visual
---

```{r}
library(tidyverse)

# Read in the data 
#| message: false
wncaa <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/wncaa.csv")

# Glimpse the data 
glimpse(wncaa)
```

Question 1

```{r}
filter_wncaa <- wncaa |>
  filter(tourney_finish == "Champ")
```

```{r}
tourn_percent <- filter_wncaa |>
  group_by(school) |>
  summarise(wins = n() * 100) |>
  mutate(percentage_w = (wins/sum(wins)) * 100) |>
  mutate(percentage_w = round(percentage_w, 2)) |>
  arrange(desc(percentage_w))
```

```{r}
ggplot(tourn_percent, aes(x = school, y = percentage_w)) + 
  geom_col() +
  coord_flip()
```

There are two teams that have similar win percentages and the two teams that won the most are Uconn and Tennessee.

Question 2

```{r}
champ_names <- unique(filter_wncaa$school)
```

```{r}
winners <- wncaa %>% 
  filter(school %in% champ_names)
```

```{r}
ggplot(winners, aes(x = reorder(school, seed), y = seed)) +
         geom_boxplot() +
  coord_flip()
```

```{r}
ggplot(winners, aes(x = seed, y = reorder(school, seed, na.rm=TRUE))) +
         geom_boxplot(outlier.shape = NA) +
          geom_jitter() 
```

Both Uconn and Tennessee had the highest seedings and i was a little suprised to see why Uconn was not higher than Tennessee giving that their win percentages were higher in tournament wins.

```{r}
ggplot(winners, aes(x = seed, y = reorder(school, seed, na.rm=TRUE), fill = school)) +
  geom_violin(outlier.shape = NA)+
  geom_jitter()
```

I like the box plot because i think that it is easier for me to read compared to the violin plot.

Question 3

```{r}
ggplot(winners, aes(x = seed, y = reorder(school, seed, na.rm=TRUE))) +
  geom_point(outlier.shape = NA) +
  geom_jitter()

```

This is not very effective because the points are all on top of each other.

Question 4

```{r}
winners_mean_sd <- winners |> 
  group_by(school) |> 
  summarize(across(where(is.numeric),
                   list(mean = mean,
                        sd = sd)))
```

```{r}
ggplot(winners_mean_sd, aes(x = reorder(school, reg_percent_mean), y = reg_percent_mean)) +
  geom_point() +
  coord_flip()
```

Texas A&M was the tournament winner but they had they lowest regular season win percentage and UConn had the highest win percentage in regards to all the other schools.

```{r}
ggplot(winners_mean_sd, aes(x = reorder(school, reg_percent_mean), y = reg_percent_mean)) +
  geom_pointrange(aes(ymin = reg_percent_mean - reg_percent_sd,
                      ymax = reg_percent_mean + reg_percent_sd)) +
  coord_flip()
```

Texas A&M has the narrowest interval this indicates that, when compared to the other colleges, the school's  win percentages each season were the closest to its average win percentage.

```{r}
ggplot(winners_mean_sd, aes(x = reorder(school, reg_percent_mean), y = reg_percent_mean)) + geom_linerange(aes(ymin = reg_percent_mean - reg_percent_sd,                                            ymax = reg_percent_mean + reg_percent_sd))+
  coord_flip()
```

I don't quite agree with the idea because there is not a way for me to find the average win percentage.
