---
title: "Untitled"
Author: Terry Moore
format: html
editor: visual
embed-resources: true
---

## Question 1

```{r}
#| message: false
library(tidyverse)
# Read in the data 
exercise_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/visualize_data.csv")
glimpse(exercise_data)
```

I think that there will be a negative relationship between peoples BMI and exercise

```{r}
cor(exercise_data$Exercise, exercise_data$BMI)
```

Since the outcome is -0.064 this proves my hypothesis to be write that there is a negative relationship between peoples BMI and exercise.

```{r}
ggplot(exercise_data, 
       aes(x = Exercise, y = BMI)) +
       geom_point() 
```

I see either a dinosaur or crocodile which is not what i expected.

## Question 2

```{r}
#|message: false
library(causact)
glimpse(corruptDF)
```

```{r}
?corruptDF
```

The CPI2017 variable indicates the public sector corruption levels in a country or territory in 2017 on a scale from 0-100. While the The HDI2017 variable tracks national progress in 2017 in the key categories of human development.

## Question 3

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017)) +
  geom_point() +
  labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017")

```

This plot shows that there is a positive relationship between HDI and CPI in 2017.

## Question 4

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme")
```

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017)) +
  geom_point() +
  geom_smooth(method = "gam", se = FALSE) +
  labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme")
```

The generalized additive model curves based on the data, while the linear model is linear. This is how the models differ from one another. However i find the linear model to be easier to use.

## Question 5

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017, fill = region, color = region)) +
  geom_point() +
  geom_smooth(method = "gam", se = FALSE) +
    labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme")
```

In 2017, I see that the intensity of the positive correlation between CPI and HDI levels varies by location and the patterns are not very clear on the graph so i think to help solve this issue you could use the facet wrap function by region to help clear up the image.

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017, fill = region, color = region)) +
  geom_point() +
  geom_smooth(method = "gam", se = FALSE) +
  labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017 by Region", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme") +
  facet_wrap(~region)
```

## Question 6

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017, fill = region, color = region)) +
  geom_point() +
  geom_smooth(method = "gam", se = FALSE) +
  facet_wrap(~region) +
 labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017 by Region", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme") +
  scale_x_reverse()
```

I thought the scale_x_reverse function because it shows that there is a lower human development if there is a high amount of corruption.

## Question 7

```{r}
ggplot(corruptDF, aes(x = CPI2017, y = HDI2017, fill = region, color = region)) +
  geom_point() +
  geom_smooth(method = "gam", se = FALSE) +
  facet_wrap(~region) +
  labs(x = "CPI", y = "HDI", title = "Relationship Between CPI and HDI in 2017 by Region", subtitle = "Data Points are Associated with Countries", caption = "Sources: Transparency International and United Nations Development Programme") +
  scale_x_reverse()
```

## Question 8

```{r}
ggsave(filename = "CPI_HDI_Scatterplot_2017.pdf")

```
