---
title: dv 4
author: Terry Moore
format: html
embed-resources: true
editor: visual
---

## Question 1

```{r}
#| message: false
library(tidyverse)

# Read in the data 
tv_ratings <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/tv_ratings.csv")

# Glimpse the data 
glimpse(tv_ratings)
```

```{r}
tv_long <- tv_ratings %>% 
  group_by(title) %>% 
  summarise(num_seasons = n()) %>% 
  ungroup() %>% 
  left_join(tv_ratings, by = "title") 

tv_long <- tv_long %>% 
  filter(num_seasons >= 5)
```

```{r}
ggplot(tv_long, aes(x = seasonNumber, y = av_rating, group = title)) +
  geom_line()
```

I can not draw any conclusions from this graph because it is very messy.

## Question 2

```{r}
ggplot(tv_long, aes(x = seasonNumber, y = av_rating, group = title)) +
  geom_line() +
  facet_wrap(~genres)
```

coord_flip function flips the coordinates from the x axis to the y axis

Question 3

```{r}
tv_ratings_nine <- tv_ratings |>
  filter(av_rating >= 9)
```

```{r}
ggplot(tv_ratings_nine, aes(x = genres)) +
  geom_bar()
```

```{r}
ggplot(tv_ratings_nine, aes(x = genres)) +
  geom_bar() +
  coord_flip()
```

The cord_flip function flips the coordinates from the x axis to the y axis.

Drama is the genre with the most top rated shows.

Question 4

```{r}

comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas)
```

```{r}
ggplot(comedies_dramas, aes(x = av_rating,
                            group = genres,
                            color = genres)) +
  geom_density()
```

The Drama genre does have a higher amount of shows that have a higher rating than Comedy..

## Question 5

```{r}
ggplot(comedies_dramas, aes(x = av_rating,
                            group = genres,
                            fill = genres)) +
  geom_histogram(position = "dodge")
```

It informs me that there are more comedy shows than drama shows, based on the number of shows that were counted

```{r}
ggplot(comedies_dramas, aes(x = av_rating,
                            group = genres,
                            color = genres)) +
  geom_freqpoly()
```

## Question 6

```{r}
ggplot(comedies_dramas, aes(x = av_rating, y = share)) +
  geom_bin_2d()
```

```{r}
ggplot(comedies_dramas, aes(x = av_rating, y = share, fill = genres)) +
  geom_bin_2d()
```

I see that in contrast to the Comedy shows the Drama genres often was dominant in the lower "share" numbers.
